Millions of Type Errors

### 2023-09-13 programming23/paper.tex
Tidying up telemetry design

\subsection{When are we logging?}

\begin{itemize}
  \item
    Collect metrics instead of source code: lines, modules, num errors
  \item
    Track an edit range to compare type errors with edits,
    use a coarse $[min, max]$ interval for speed
  \item
    Count specific errors only for the current edit range
    (reduces size of logs)
  \item
    Within the edit range, collect data before and after the latest edits.
  \item
    Log randomly on keystroke instead of per specific event.
    One exception: log module switches because that helps discover
    codebases that use several analysis modes.
    Randomness helps lower the amount of data.
  \item
    Observe sessions randomly (again to lower the amount of data).
\end{itemize}

TODO must explain edit range carefully.

\subsection{What are we logging?}

\FILL{} change to long-form paragraphs, use more space for examples

\begin{description}
  \item[D1] metadata: uid, timestamp, session duration
  \item[D2] mode (\mnocheck{}, \mnonstrict{}, \mstrict{})
  \item[D3] a 1-bit reason for sending: did the user switch module?
    \subitem we get logs for two reasons: (1) switch module, (2) randomly with
    low probability after typechecking
  \item[D4] size of codebase: num files, num lines
  \item[D5] size of edit range
  \item[D6] overall type errors: for old and curr states, have: \# total, \# in module, and \# in range
  \item[D7] specific errors in the edit range: in the edit range, for old and
    curr states, how many type errors for each type error code? (There is 1
    edit range per log.)
    \subitem Examples, if the old state had one type-A error:
    \begin{itemize}
      \item If the latest edits touched it and fixed it, the next log says 1
        old type-A and 0 new type-A
      \item touched it, didn't fix => 1 old-A, 1 new-A
      \item didn't touch (fixed or not) => 0 old-A, 0 new-A
    \end{itemize}
  \item[D8] ForcedStrict "what if" errors for \mnocheck{}: specific errors for the
    edit range computed as if the user had strict mode enabled (even though they
    have no-check enabled)
    \subitem This info is available because it gives better hints for
    autocomplete, because it assumes precise types for ALL libraries (rather
    than Any)
  \item[D9] TooComplexErrors: project-wide count for this one specific error type
\end{description}

>>>>

\subsection{Telemetry records}

The telemetry for a Roblox Studio session is gathered as a series of
telemtry records, all with the same psedonynimized session
identifier. This allows us to correlate telemetry across a single
session, but not between sessions.

In order to avoid swamping our telemtry servers, we randomly throttle
the generation of telemetry records:
\begin{itemize}
  \item
    10\% of Roblox Studio sessions were enrolled in generating telemetry, and
  \item
    5\% of runs of the typechecker in an enrolled session generated a telemetry record.
\end{itemize}
In order to find how file-switching correlated with type errors, we additionally have:
\begin{itemize}
  \item
    every run of the typechecker in an enrolled session which switched file generated a telemetry record.
\end{itemize}
Each telemetry record contains:
\begin{description}
  \item[D1] metadata: a psedonymized session identifier, timestamp and session duration,
  \item[D2] mode of the current file: (\mnocheck{}, \mnonstrict{}, or \mstrict{}),
  \item[D3] reason for sending: (random selection, or file switch),
  \item[D4] size of codebase: number of files, and number of lines of code type checked,
  \item[D5] size of edit range
  \item[D6] overall type errors: for previous and current states, we have the total number, the nunber in the current file, and number in the edit range,
  \item[D7] specific errors in the edit range: for the previous and current states, for each type error code, the number type errors in the edit range,
  \item[D8] forced strict errors: specific errors for the
    edit range computed as if the user had strict mode enabled.
  \item[D9] TooComplexErrors: project-wide count for this one specific error type
\end{description}
To track the edit range, we record a start and end position, which we
update appropriately on every edit. This can result in very large edit
ranges (for example if the user edits an the beginning and end of the
file) but fits in a fixed-size telemetry record.
